### 2014-02-10 paper/appendix.tex
added more bib, fleshed out a few things, put some tables

\section{Objet 260 Connex Digital Materials}
Softer materials (concentration of > 65% Tango-series material) do not easily accept the copper paint (it cracks when bent and is easy to wash off).  This may preclude flex sensors made of interior copper paint (conductive thread or other materials may be able to be used for some parts of this).

>>>>

\section{Objet 260 Connex Digital Materials}
Softer materials (concentration of $> 65\%$ Tango-series material) do not easily accept the copper paint (it cracks when bent and is easy to wash off).  This may preclude flex sensors made of interior copper paint (conductive thread or other materials may be able to be used for some parts of this).

\section{Bend Radius Measurements}
\begin{itemize}
\item EL wire diameter 2.3mm: minimum bend radius .35in = 8.89mm
\item Water: uh.  None?
\item Muscle Wire: ?
\item Fiber Optic Cable: ?
\end{itemize}

### 2014-02-10 paper/relatedwork.tex
added more bib, fleshed out a few things, put some tables

\section{Related Work}
This should be thought about soon!

@@

\begin{table*}[t]
\begin{tabular}{ r || p{3cm} | p{3cm} | p{3cm} | p{3cm} }
  \hline
   & Gas & Liquid & Particles & Threadables\\ \hline \hline
  Visual & \parbox{3cm}{PneUIs, \\Harrison latex thingy, \\ \emph{smoke display}} & \parbox{3cm}{Splash Controllers, \\ \emph{paint mixer}} &\parbox{3cm}{\emph{clear thing with popcorn}} &\parbox{3cm}{\emph{neon sign}} \\ \hline
  Aural & \parbox{3cm}{\emph{resonance}} & \parbox{3cm}{} &\parbox{3cm}{\emph{CNC maracas}} &\parbox{3cm}{} \\ \hline
  Tactile/Haptic & \parbox{3cm}{PneUIs,\\ \emph{haptic textures}} & \parbox{3cm}{Splash Controllers,\\ \emph{warm/cold liquid}} &\parbox{3cm}{Jamming UIs, \\ \emph{sparse particle haptic textures}} &\parbox{3cm}{Otherlab robots} \\ \hline
  Olfactory/Gustatory & \parbox{3cm}{\emph{scents}} & \parbox{3cm}{\emph{smoothie mixer!}} &\parbox{3cm}{} &\parbox{3cm}{} \\ \hline
  Touch Input & \parbox{3cm}{Harrison latex thingy} & \parbox{3cm}{Harrison SFCS, \\ \emph{injectable capacitive sensors}} &\parbox{3cm}{Jamming UIs} &\parbox{3cm}{\emph{capacitance on wires}} \\ \hline
  Pressure Input & \parbox{3cm}{Slyper printed doodads} & \parbox{3cm}{\emph{capacitance, flow meter}} &\parbox{3cm}{} &\parbox{3cm}{} \\ \hline
  Other Input & \parbox{3cm}{Slyper (twist, bend, flex, etc.), \\ \emph{printed flex sensors}} & \parbox{3cm}{} &\parbox{3cm}{} &\parbox{3cm}{\emph{use traditional components}} \\ \hline
\end{tabular}
\end{table*}

>>>>

\section{Related Work}

\begin{itemize}
\item \cite{Sarik-tracebrush} - this uses an airspray machine to add conductive paths to surface of 3D prints
\item \cite{Harrison-buttons} - fabricate latex + acrylic buttons and pressurize with air
\item \cite{Hashimoto-squirming} - hold a speaker in your hands, and air pressure changes make it feel like you're holidng a living, squirming thing
\item \cite{Kim-inflatablemouse} - a basic mouse, but it inflates so you can store it and also use it more reasonably than a flat mouse
\item \cite{Ono-touchandactivate} - the Touch\'{e} with sound paper from last year's UIST
\item \cite{Iwata-volflex} - a display made up of many balloons that inflate and deflate to change the shape
\item \cite{Sells-reprap} - the RepRap people using a syringe of hot solder to squirt flat circuits into flat channels
\item \cite{Majidi-curvature} - inject liquid metal into really thin tubes in a soft substrate, sense stretching by changing resistance
\item \cite{Navarrette-gps} - I'm a little unclear on what they did, but they fabbed something with a "3D circuitboard" that has a bypass that goes into 3D.  they don't offer a routing algorithm or anything, though.
\item \cite{Optomec} - fancy machines that spray conductive film
\item \cite{Slyper-pressure} - robots that are made of squishy stuff where air pressure changes are sensed.  input components designed to react to different manipulations (pushing, squeezing, twisting, etc.)
\item \cite{icecats-conductivepaint} - an instructable I followed to make my first batch of conductive paint
\item \cite{Follmer-jamming} - Jamming User Interfaces
\item \cite{Park-microchannels} - similar to injection of liquid metal, above
\item \cite{Slyper-shape} - creating silicone bendy things with embedded electronics to sense flexing, stretching, etc., supported by those shapes.
\item \cite{Yao-pneui} - PneUIs, creating interfaces with pneumatics
\item \cite{Willis-infrastructs} - InfraStructs, identification of 3d printed objects using Terahertz imaging
\item \cite{Willis-printedoptics} - Printed Optics.  doing cool stuff with clear material (touch sensing and display)
\item \cite{Sodhi-aireal} - air vortex generation in free space.  air haptics.
\item \cite{Savage-midas} - Midas.  routing in 2D to connect up capacitive sensors
\item \cite{Savage-sauron} - Sauron.  computer vision of mechanical components obviates electronics installation.
\item \cite{Sato-touche} - Touch\'{e}.  It's like Touch\'{e} with sound, but without sound.  SFCS.
\end{itemize}

@@

\begin{table*}[t]
\caption{Existing systems are written in regular font.  What's in \emph{italic} are things that I think we could make.  I don't know what else might go in the blank spaces... looking for suggestions!  Also, I'm not confident this breakdown is the most clear: for example, the "liquids" category includes the copper paint, which functions as wires ("threadables"), but takes the form of a liquid...}
\begin{tabular}{ r || p{3cm} | p{3cm} | p{3cm} | p{3cm} }
  \hline
   & Gas & Liquid & Particles & Threadables\\ \hline \hline
  Visual & \parbox{3cm}{PneUIs, \\Harrison latex thingy, \\ \emph{smoke display}} & \parbox{3cm}{Splash Controllers, \\ \emph{paint mixer}} &\parbox{3cm}{\emph{clear thing with popcorn}} &\parbox{3cm}{\emph{neon sign}} \\ \hline
  Aural & \parbox{3cm}{\emph{resonance}} & \parbox{3cm}{\emph{bubbling/splashing noises}} &\parbox{3cm}{\emph{CNC maracas}} &\parbox{3cm}{} \\ \hline
  Tactile/Haptic & \parbox{3cm}{PneUIs,\\ \emph{haptic textures}} & \parbox{3cm}{Splash Controllers,\\ \emph{warm/cold liquid}} &\parbox{3cm}{Jamming UIs, \\ \emph{sparse particle haptic textures}} &\parbox{3cm}{Otherlab robots} \\ \hline
  Olfactory/Gustatory & \parbox{3cm}{\emph{scents}} & \parbox{3cm}{\emph{smoothie mixer!}} &\parbox{3cm}{} &\parbox{3cm}{} \\ \hline
  Touch Input & \parbox{3cm}{Harrison latex thingy} & \parbox{3cm}{Harrison SFCS, \\ \emph{injectable capacitive sensors}} &\parbox{3cm}{Jamming UIs} &\parbox{3cm}{\emph{capacitance on wires}} \\ \hline
  Pressure Input & \parbox{3cm}{Slyper printed doodads} & \parbox{3cm}{\emph{capacitance, flow meter}} &\parbox{3cm}{} &\parbox{3cm}{} \\ \hline
  Other Input & \parbox{3cm}{Slyper (twist, bend, flex, etc.), \\ \emph{printed flex sensors}} & \parbox{3cm}{\emph{use traditional components}} &\parbox{3cm}{} &\parbox{3cm}{\emph{use traditional components}} \\ \hline
\end{tabular}
\end{table*}
\

### 2014-02-10 paper/tubes.tex
added more bib, fleshed out a few things, put some tables

@@

\begin{itemize}
\item Gas (compressible).  Air with smells.  Air with fog.
\item Liquid (incompressible).  Clear, colored, conductive, heated, flavored (smoothie!).  Fill or coat.
\item Particles.  Sparse for haptic feedback.  Dense for jamming.
\item Threadables.  EL wire, conductive wire, fiberoptic cable, muscle wire.
\end{itemize}

@@

\textbf{designing interior paths}

\textbf{designing exterior connection points}

@@

\subsubsection{Touch}
Capacitance (digital).

@@

\subsubsection{Tapping}
 Tapping (audio/resonance?) carried through particular tubes, like we talked about hard tubes in a soft thing.

@@

\subsubsection{Visual}
EL wire.  Colored liquids.  Mechanical motion by pushing light stuff with air.

>>>>

\subsection{Topology of Tubes}

\begin{itemize}
\item splitting - one tube becomes two (e.g., for grounding several components)
\item mixing - two tubes become one (e.g., for mixing liquids)
\item star - several tubes meet at a point (good for mixing I guess?)
\item tree - a.. tree.  easy to inject with goo.
\end{itemize}

@@

\begin{itemize}
\item Gas (compressible).  Air with smells.  Air with fog.
\item Liquid (incompressible).  Clear, colored, conductive, heated, flavored (smoothie!).  Fill or coat.
\item Particles.  Single for games/display.  Sparse for haptic feedback.  Dense for jamming.
\item Threadables.  EL wire, conductive wire, fiberoptic cable, muscle wire.
\end{itemize}

@@

\textbf{designing interior paths} -- take into account bend radius of desired material

\textbf{designing exterior connection points} -- focus on either \emph{shape} or \emph{location}

\subsubsection{Fabrication Techniques}

\textbf{printing} - different strategies with Objet (all print-in-place) and Makerbot (may need to add things like balloons afterwards).  Ryan just got flexible material, we should see how stretchy it is...!  We could also consider assembleable things that are easier to create using parts that clip together... probably out of scope.

\textbf{hand tools} - post-fabrication modification is possible using hand tools.  We can mark the surface to show where conduits are and how deep.  I can also use this to test things beforehand.

@@

\subsubsection{Touch}
Capacitance (digital).  SFCS (possible with mixed resistance things).

@@

\subsubsection{Tapping}
 Tapping (audio/resonance?) carried through particular tubes, like we talked about hard tubes in a soft thing.  We use hard tubes in soft things, anyway, for the conductive goo.

@@

\subsubsection{Visual}
EL wire.  Colored liquids.  Mechanical motion by pushing light or plugging (like a big ball) stuff with fluid.
